Toward dynamic models of combat or lack thereof in animal mating

### 2015-12-22 ms.tex
Add references, subsections
figure explanations and Triats

\subsection{Introduction}

@@

\subsection{Methods}

>>>>

\section{Introduction}

@@

\section{Methods}

\subsection{Population dynamics}

\subsection{Encounters}

\subsection{Evolutionary dynamics}

\subsection{Numerical analysis}

\section{Figures}
Figure 1. Event Algorithm
Population state generates events, events are either:
\begin{enumerate}
    \item A new individual x has matured and entered the contest (based off of a trait(?))
    \item Discovery event wherin both a nest RR (repoductive resource) and an individual x are drawn from a pool, that nest is either:
\begin{enumerate}
    \item un-occupied: in which x takes ownership of RR.
    \item occupied by x' in which a constest occurs (see fig 2)
\end{enumerate}
\end{enumerate}
After the contest Energy costs are deducted from both the winner and the loser.
The winner also has a chance to abandon the RR (based off a trait).
If a death occurs (Energy(x) < 0) then x is removed from the individual pool.

Figure 2. Contest Algorithm
for an occupier x' vs an invader x, there are 3 stages:
\begin{enumerate}
    \item Display 1
    \item Display 2
    \item Fight
\end{enumerate}
In the display phases the probability of escalation is dependant on the visible traits of x and x'
The rate of events increases as time t -> t1

Traits:
\begin{enumerate}
    \item Visible to opponent:
\begin{enumerate}
    \item Size
\end{enumerate}
    \item invisible to opponent:
\begin{enumerate}
    \item Energy levels
    \item Abandon Rate
    \item Aggression
    \item Encounter Rate
    \item Experience (?)
\end{enumerate}
\end{enumerate}
